\EVOSUITE at the SBFT 2023 Tool Competition

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Switch from acmart to IEEEtran

%\documentclass[sigconf,review,anonymous]{acmart}
\documentclass[sigconf]{acmart}

@@

\copyrightyear{2022}
\acmYear{2022}
\setcopyright{acmcopyright}
\acmConference[SBST'22 ]{The 15th Search-Based Software Testing Workshop}{May 9, 2022}{Pittsburgh, PA, USA}
\acmBooktitle{The 15th Search-Based Software Testing Workshop (SBST'22 ), May 9, 2022, Pittsburgh, PA, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3526072.3527526}
\acmISBN{978-1-4503-9318-8/22/05}

@@

\author{Sebastian Schweikl}
\affiliation{%
  \institution{University of Passau}
  \city{Passau}
  \country{Germany}
}
%\email{gordon.fraser@uni-passau.de}

\author{Gordon Fraser}
\affiliation{%
  \institution{University of Passau}
  \city{Passau}
  \country{Germany}
}
%\email{gordon.fraser@uni-passau.de}

\author{Andrea Arcuri}
\affiliation{%
  \institution{Kristiania University College and Oslo Metropolitan University}
  \city{Oslo}
  \country{Norway}
}
%\thispagestyle{empty}

>>>>

\documentclass[10pt,conference]{IEEEtran}

@@

@@

\author{%
  \IEEEauthorblockN{Sebastian Schweikl}
  \IEEEauthorblockA{%
    \textit{University of Passau} \\
    Passau, Germany \\
    email address or ORCID
  }
  \and
  \IEEEauthorblockN{Gordon Fraser}
  \IEEEauthorblockA{%
    \textit{University of Passau} \\
    Passau, Germany \\
    email address or ORCID
  }
  \and
  \IEEEauthorblockN{Andrea Arcur}
  \IEEEauthorblockA{%
    \textit{Kristiania University College and Oslo Metropolitan University} \\
    Oslo, Norway \\
    email address or ORCID
  }
}
